---

title: "All Calls"
author: "Fiona Spooner"
date: "25 October 2019"
output: html_document
---
```{r}
library(bbmle)
library(chron)
library(data.table)
library(DHARMa)
library(dplyr)
library(ggplot2)
library(glmmTMB)
library(here)
library(jsonlite)
library(lubridate)
library(scales)
library(suncalc)
library(tidyr)
library(vroom)

```


```{r, eval=FALSE}

#dump<-read.table("qeop_dump_all.csv", fill=T, sep=",")

dump_test<-read.table("qeop_dump_2019_02_23.csv", fill=T, sep=",")


dump<-read.table("all_bat_2019_09_02a.csv", fill=T, sep=",",skip = 4)
dumpb<-read.table("all_bat_2019_09_02b.csv", fill=T, sep=",", skip = 1)

dump_all<-rbind(dump, dumpb)


##adding in a column to identify each row with a sensor

dump_all$sensor<-NA
for (i in 1:15){
  start_id<-min(which(grepl( paste("qeop_batstore_",i, sep=""),dump_all[,1])))
  end_id<-max(which(grepl( paste("qeop_batstore_",i, sep=""),dump_all[,1])))
  dump_all[start_id:end_id,]$sensor<-paste("Sensor_",i,sep="")
  print(i)
}

table(dump_all$sensor)

dump_all$sensor[1:776]<-1

dump_all$sensor[1638302:1639016]<-7

dump<-dump_all[!is.na(dump_all$sensor),]

dump<-dump[,c(1,2,4,5,6,13,ncol(dump))]
dump<-dump[grepl("\t",dump[,1]),]
dump[,1]<-as.numeric(gsub("[\t(]","",dump[,1]))
dump[,3]<-as.numeric(gsub("[^0-9.]", "",  dump[,3]))
dump[,4]<-as.numeric(gsub("[^0-9.]", "",  dump[,4]))
dump[,5]<-gsub("[[:punct:]]", "", dump[,5])
dump[,5]<-substring(dump[,5],2)
dump[,6]<-as.numeric(gsub("[^0-9.]", "",  dump[,6]))

dump$sensor_no<-as.numeric(gsub("[^0-9.]", "",  dump$sensor))

colnames(dump)<-c("ID", "datetime", "prob_bat","prob_sp","species_class","call_time","sensor", "sensor_no")

dump$datetime<-as.POSIXct(dump$datetime,format="%Y-%m-%d %H:%M:%S")

dump$date<- as.Date(dump$datetime)

dump$species_class<-substring(dump$species_class, 2)


dump$time<- format(dump$datetime, "%H:%M:%S")


#write.csv(dump, "all_ce_tools_dump_2019_09_02a.csv", row.names = FALSE)

```



```{r, eval= FALSE , echo = FALSE}

library(stringr)

os_dirs<-list.dirs(here::here("data_archive/opensensors_Daniyar/qeoplogs_more/"))

getmode<-function(v){
  uniqv<-unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}

#getting rid of the folders with multiple dates in - removing anything which doesn't have the modal average number of characters. Bit shaky but okay for now.
os_dirs<-os_dirs[nchar(os_dirs)==getmode(nchar(os_dirs))]


os_tool_out<-function(os_dir){
  file_list<-list.files(os_dir)
  
  for (file in file_list){
      print(os_dir)
      print(file)
    
      if(grepl(".csv", file)){
         df_temp = read.table(paste(os_dir,"/", file, sep=""), sep=",", header = T, stringsAsFactors = F)
         df_temp$sensor_id<-as.numeric(gsub("\\D", "", file))
         df_temp$timestamp<-as.numeric(as.character(df_temp$timestamp))
         df_temp$timestamp<-anytime(df_temp$timestamp/1000)
         
         df_out<-df_temp[,c("sensor_id","timestamp", "call_time", "prob_bat", "c1", "p1")]
         
      } 
    
      if (grepl(".txt", file)) {
         #df_temp = read.table(paste(ce_dir,"/", file, sep=""))
         df_temp = read.csv(paste(os_dir,"/", file, sep=""), header = FALSE)
         cols<-paste("V", 1:ncol(df_temp), sep="")
         df_temp$x <- apply( df_temp[ , cols ] , 1 , paste , collapse = "." )
         
         spl<-strsplit(df_temp$x, " ")
         
         get_neat_os_data<-function(x){
           
             sensor_id<-gsub("[^0-9]", "", x[which(grepl("sensor_bat",x))])
             
             timestamp<-gsub("[^0-9.]", "",paste(x[which(x== "timestamp:")+1],x[which(x== "timestamp:")+2],x[which(x== "timestamp:")+3],x[which(x== "timestamp:")+4], x[which(x== "timestamp:")+5], x[which(x== "timestamp:")+6], sep=""))
             
             timestamp<-toString(strsplit(timestamp, "[.]")[[1]][2:7])
             
             timestamp<-as.POSIXct(timestamp, format = "%Y, %m, %d, %H, %M, %S")  
             call_time<-x[which(x == "call_time:")+1]
             call_time<-as.numeric(substr(call_time, 1, nchar(call_time)-1)) 
             
             prob_bat<- x[which(x == "prob_bat:")+1]
             prob_bat<-as.numeric(substr(prob_bat, 1, nchar(prob_bat)-1))  
              
             genus<-gsub("'","",x[which(x == "c1:")+1])
             spec<-gsub("[[:punct:]]","",x[which(x == "c1:")+2])
             
             c1<-paste(genus, spec, sep = " ")
             
             p1<- x[which(x == "p1:")+1]
             p1<-as.numeric(substr(p1, 1, nchar(p1)-1)) 
             
             df_out<-data.frame(sensor_id,timestamp, call_time, prob_bat, c1, p1)
             colnames(df_out)<-c("sensor_id","timestamp", "call_time", "prob_bat", "c1", "p1")
             print(df_out)
         return(df_out)
         }
         
         df_out<-lapply(spl,get_neat_os_data)
         df_out<-do.call("rbind", df_out)
         
           }
         #print(os_dir)
         #print(file)
         df = rbind(df, df_out)
         #print(paste(os_dir, file, sep="/"))
        
          }
  
  return(df)
}

df<-data.frame()

os_df<-lapply(os_dirs, os_tool_out)



colnames <- c("sensor_id","timestamp", "call_time", "prob_bat", "c1", "p1") 


# for (i in seq_along(os_df)){
#   
#   if(length(colnames(os_df[[i]])) > 0){
#   colnames(os_df[[i]]) <- colnames
#   } else{
#     os_df[[i]]<-NULL
#   }
#   print(i)
#   }


os_sens_df<-do.call("rbind", os_df)

os_sens_df$c1<-gsub('[[:punct:] ]+',' ',os_sens_df$c1)

os_sens_df$c1<-str_trim(os_sens_df$c1)


os_sens_df$date<-as.Date(os_sens_df$timestamp)

os_sens_df$time<-format(os_sens_df$timestamp, "%H:%M:%S")




#write.csv(os_sens_df, "all_sensors_os_records_May_2019.csv", row.names = FALSE)

```


```{r, eval=FALSE, echo = FALSE}

os_sens_df<-vroom::vroom("all_sensors_os_records_May_2019.csv")
ce_sensors<-vroom::vroom("all_ce_tools_dump_2019_09_02a.csv")

ce_sensors<-ce_sensors %>% 
              dplyr::select(sensor_no, datetime, call_time,prob_bat, species_class, prob_sp,date, time)

colnames(ce_sensors)<-colnames(os_sens_df)
#ce_sensors$sensor_id<- gsub("[^0-9.]", "", ce_sensors$sensor_id)

all_calls_df<-rbind(ce_sensors, os_sens_df)

sensor_info<-read.csv("sensor_info.csv")
sensor_info$sensor_id<-gsub("\\..*","",sensor_info$deployment_id)

all_sens_info<-merge(all_calls_df, sensor_info, by = "sensor_id")


#write.csv(all_sens_info, "all_sensors_info_records_2019_10_25.csv", row.names = FALSE)

```



Adding deployment information column

```{r, echo = FALSE,eval = FALSE}
all_sens_info<-vroom::vroom("all_sensors_info_records_2019_10_25.csv")

all_sens_info$deployment<-1

all_sens_info[as.Date(as.character(all_sens_info$date)) > as.Date(as.character("2018-05-14")) & all_sens_info$sensor_id == 4,]<-all_sens_info %>%
  filter(as.Date(as.character(date)) > as.Date("2018-05-14") & sensor_id == 4)%>%
  mutate(deployment=replace(deployment, deployment==1, 2), Lat = replace(Lat, Lat==51.5367, 51.536553), Lon = replace(Lon, Lon==-0.0128, -0.013169))

all_sens_info[as.Date(as.character(all_sens_info$date)) > as.Date("2018-08-07") & all_sens_info$sensor_id == 5,]<-all_sens_info %>%
  filter(as.Date(as.character(date)) > as.Date("2018-08-07") & sensor_id == 5)%>%
  mutate(deployment=replace(deployment, deployment==1, 2), Lat = replace(Lat, Lat==51.5362, 51.590616), Lon = replace(Lon, Lon==-0.0127, -0.0139243), Habitat = replace(Habitat, Habitat == "Grassland", "Duncan's Garden" ))


all_sens_info$deployment_id<-paste(all_sens_info$sensor_id, all_sens_info$deployment, sep = ".")

```

```{r, echo = FALSE,eval = FALSE}
all_sens_info$month<-months.Date(as.Date(all_sens_info$date))

all_sens_info$month<-factor(all_sens_info$month, levels = month.name)

all_sens_info$timestamp<-as.POSIXct(all_sens_info$timestamp)

t <- strftime(all_sens_info$timestamp, format="%H:%M:%S")

all_sens_info$time<-as.POSIXct(t, format="%H:%M:%S")

all_sens_info<-all_sens_info[complete.cases(all_sens_info),]

all_sens_info$Habitat<-as.character(all_sens_info$Habitat)

all_sens_info$date_ch<-as.character(all_sens_info$date)

all_sens_info$c1<-as.character(all_sens_info$c1)

all_sens_info$month_ch<-all_sens_info$month

all_sens_info<-all_sens_info %>%
  group_by(sensor_id,c1, date)%>%
  mutate(count_sp = n())%>%
  ungroup()

all_sens_info<-all_sens_info %>%
   mutate(c1 = replace(c1, c1 == "yctalus leisleri", "Nyctalus leisleri"))%>%
   mutate(c1 = replace(c1, c1 == "yctalus noctula", "Nyctalus noctula"))%>%
   mutate(c1 = replace(c1, c1 == "ipistrellus nathusii", "Pipistrellus nathusii"))%>%
   mutate(c1 = replace(c1, c1 == "ipistrellus pipistrellus", "Pipistrellus pipistrellus")) %>% 
   mutate(c1 = replace(c1, c1 == "ipistrellus pygmaeus", "Pipistrellus pygmaeus")) %>% 
   mutate(c1 = replace(c1, c1 == "lecotus auritus", "Plecotus auritus")) %>% 
   mutate(c1 = replace(c1, c1 == "lecotus austriacus", "Plecotus austriacus")) %>% 
   mutate(c1 = replace(c1, c1 == "yotis brandtii", "Myotis brandtii")) %>% 
   mutate(c1 = replace(c1, c1 == "yotis daubentonii", "Myotis daubentonii")) %>% 
   mutate(c1 = replace(c1, c1 == "yotis nattereri", "Myotis nattereri"))

all_sens_info<-all_sens_info %>%
  group_by(date_ch)%>%
  mutate(count_date = n())%>%
  ungroup()

all_sens_info<-all_sens_info %>%
  mutate(hour_rnd = round_date(timestamp, unit = "hour"), hour_u = hour(timestamp))%>%
  group_by(hour_rnd, deployment_id)%>%
  mutate(count_hour_dep_rnd = n()) %>%    #call count per rounded hour per deployment
  ungroup()



#vroom_write(all_sens_info, "all_sensors_all_callsb.csv", delim = ",")

```

####Figure 5: Distribution of total daily calls for each month 

```{r,eval = FALSE}
all_sens_info<-vroom("all_sensors_all_callsb.csv")

hourly_sum<-all_sens_info %>% 
  select(sensor_id, deployment_id, Lat, Lon, date, hour_rnd, count_hour_dep_rnd) %>% 
  distinct()

start<-min(all_sens_info$hour_rnd)
end<-max(all_sens_info$hour_rnd)

hourly_seq<-seq(start, end, by = "hour")
#names(hourly_seq)<-c("hour_rnd")

sensors<-unique(select(all_sens_info, c("sensor_id", "deployment_id", "Lat", "Lon")))

hourly_sens_seq<-rep(hourly_seq, times = length(sensors$deployment_id))
deployment_sens_seq<-rep(sensors$deployment_id, each = length(hourly_seq))

df_seq<-data.frame(hourly_sens_seq, deployment_sens_seq)
colnames(df_seq)<-c("hour_rnd", "deployment_id")

rnd_seq<-merge(df_seq,hourly_sum, by = c("hour_rnd","deployment_id"), all = TRUE)

rnd_df<-rnd_seq %>% 
  group_by(deployment_id) %>%
  arrange(sensor_id) %>% 
  tidyr::fill(sensor_id, Lat, Lon) %>% 
  ungroup() %>% 
  mutate(date = date(hour_rnd))
 

#write.csv(rnd_df, "hourly_counts_all_sensors.csv", row.names = FALSE)
  
```

Weather data


```{r, eval = FALSE}
files<-list.files(here::here("/data_archive/weather_data/pws2017timberhourly"), full.names = TRUE, pattern = "*.json")

files<-files[grepl("/20", files)]


json2df<-function(json){

  # Give the input file name to the function.
  if(!is.null(count.fields(json))){
    result <- fromJSON(txt = json)
    
    # Convert JSON file to a data frame.
    json_data_frame <- as.data.frame(result)
    json_data_frame <- data.frame(json_data_frame[,-15],json_data_frame$observations.metric)
    
    print(json)
    return(json_data_frame)    
  }
  
}

json_out<-lapply(files, json2df) # 25th may 2017 empty file need a catch for that

json_df<-do.call("rbind", json_out)
```


```{r, eval = FALSE}
json_df$observations.obsTimeUtc<- as.POSIXct(json_df$observations.obsTimeUtc, format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC")
attr(json_df$observations.obsTimeUtc, "tzone") <- "UTC" 
json_df$date<-date(json_df$observations.obsTimeUtc)

json_df$precipRate[is.na(json_df$precipRate)]<-0

daily_climate_data<-json_df%>%
  group_by(date)%>%
  summarize(mean_temp = mean(tempAvg), 
            mean_humid = mean(observations.humidityAvg), 
            mean_wind = mean(windspeedAvg), 
            mean_wind_gust = mean(windgustAvg),
            precip_total = sum(precipRate))

#write.csv(daily_climate_data, "QEOP_daily_climate_data_2019_10_28.csv", row.names = FALSE)
```


```{r, eval = FALSE}
hourly_climate_data<-json_df
hourly_climate_data$round_time<-round_date(as.POSIXct(hourly_climate_data$observations.obsTimeUtc, format = "%Y-%m-%d %H:%M:%S"), unit = "hour")

all_hours<-data.frame(seq(min(hourly_climate_data$round_time), max(hourly_climate_data$round_time), by = "hour"))
colnames(all_hours)<-"round_time"

hourly_climate_data<-hourly_climate_data%>%
  group_by(round_time)%>%
  summarize(mean_temp = mean(tempAvg), 
            mean_humid = mean(observations.humidityAvg), 
            mean_wind = mean(windspeedAvg), 
            mean_wind_gust = mean(windgustAvg),
            precip_total = sum(precipRate))

all_hours_c_data<-merge(all_hours, hourly_climate_data, by = "round_time", all = TRUE)

all_hours_c_data<-all_hours_c_data[complete.cases(all_hours_c_data),]

hourly_df_clim<-merge(rnd_df, all_hours_c_data, by.x = "hour_rnd", by.y = "round_time")


#write.csv(hourly_climate_data, "QEOP_hourly_climate_data_2019_10_28.csv", row.names = FALSE)

#write.csv(hourly_df_clim, "hourly_calls_and_climate_data_2019_10_28.csv", row.names = FALSE)

```

```{r, eval = FALSE}

hourly_df_clim<-read.csv("hourly_calls_and_climate_data_2019_10_28.csv")

break_finder<-function(x){
  nl_out<-rep(x, each = x)
  }

all_sensors_df<-NULL

for (id in unique(hourly_df_clim$deployment_id)){

  test<-hourly_df_clim[hourly_df_clim$deployment_id == id, ]
  test<-arrange(test, hour_rnd)
  rl<-rle(is.na(test$count))  
  bf_out<-sapply(rl$lengths, break_finder)
  test_na_run<-unlist(bf_out)
  test_na_run[!is.na(test$count)]<-NA
  test$hours_inactive<-test_na_run
  all_sensors_df<-rbind(all_sensors_df,test)
  print(id)
  
  }

all_sensors_df$inactive<-all_sensors_df$days_inactive

all_sensors_df$inactive_week[all_sensors_df$hours_inactive < (7*24) | is.na(all_sensors_df$hours_inactive)]<-NA

all_sensors_df$inactive_week[all_sensors_df$hours_inactive >= (7*24)]<-1

all_sensors_df$count_hour_dep_rnd[is.na(all_sensors_df$count_hour_dep_rnd)]<-0

all_sensors_df$count_hour_dep_rnd[which(all_sensors_df$inactive_week == 1)]<-NA

```

```{r}

all_sensors_df$active_week<-ifelse(is.na(all_sensors_df$inactive_week), 1, 0)
all_sensors_df$date<-as.Date(all_sensors_df$date)
all_sensors_df$hour_rnd<-as.POSIXct(all_sensors_df$hour_rnd, format = "%Y-%m-%d %H:%M:%S")
all_sensors_df$deployment_id<-as.factor(all_sensors_df$deployment_id)
all_sensors_df$month<-lubridate::month(all_sensors_df$hour_rnd, label = TRUE, abbr = TRUE)
all_sensors_df$hours_inactive[is.na(all_sensors_df$hours_inactive)]<-0
all_sensors_df$inactive_week[is.na(all_sensors_df$inactive_week)]<-0

all_sensors_df<-all_sensors_df[!is.na(all_sensors_df$hour_rnd),]  #some NAs have snuck in - not sure where from...

all_sensors_df$inactive_week[all_sensors_df$inactive_week == 0] <- NA

all_sensors_df<-all_sensors_df %>% 
  group_by(hour_rnd) %>%
  mutate(sum_active = sum(active_week),  count_ef = count_hour_dep_rnd/sum_active) %>% 
  distinct() %>% 
  ungroup()


write.csv(all_sensors_df, "all_sensors_df.csv", row.names = FALSE)

```


```{r}

year_plot<-ggplot(all_sensors_df, aes(x = month, y = count_hour_dep_rnd))+
  geom_boxplot()+
  #scale_y_continuous(trans = log10_trans(), breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x)))+
  labs(x = "Month", y = "Hourly Detected Calls")+
  scale_x_discrete(labels=month.abb) +
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 18, angle= 45, hjust = 1),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))


#png("Annual_Calls_wide.png", width = 10, height = 8, units = 'in', res = 300)
year_plot# Make plot
#dev.off()


```


```{r}

year_effort_plot<-ggplot(all_sensors_df, aes(x = month, y = count_ef))+
  geom_boxplot()+
  #scale_y_continuous(trans = log10_trans(), breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x)))+
  labs(x = "Month", y = "Hourly Detected Calls")+
  scale_x_discrete(labels=month.abb) +
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 18, angle= 45, hjust = 1),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))


#png("Annual_Calls_wide.png", width = 10, height = 8, units = 'in', res = 300)
year_effort_plot# Make plot
#dev.off()


```


```{r}

ggplot(all_sensors_df, aes(x = hour_rnd, y = deployment_id, group = deployment_id))+
  geom_line(color = "red", aes(x = hour_rnd, y = deployment_id,size = log10(inactive_week)), alpha = 0.5)+
  geom_line(color = "steelblue",aes(size = log10(count_ef)))+
    #scale_y_reverse(breaks = seq(1, 16, by = 1))+
  scale_y_discrete(limits = c("15.1", "14.1", "13.1","12.1", "11.1","10.1", "9.1", "8.1","7.1","6.1","5.2","5.1","4.2","4.1","3.1","2.1","1.1"))+
  #scale_x_date(date_breaks = "1 month", date_labels = "%m-%Y")+
  theme_bw()+
  #theme(panel.background = element_blank())+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 14, angle= 45, hjust = 1),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=18),
        legend.title=element_text(size=20))+
  labs(x = "Date", y = "Deployment", linetype = "test")+
  #scale_fill_continuous(breaks = c(0,1,2,3,4), labels = c("1","10", "100","1000","10000"), guide =guide_legend(title ="Detections\n(Log10)"))
  scale_size_continuous(breaks = c(0,1,2,3,4),labels = c("1","10","100", "1000", "10000"))+
  guides(size = guide_legend(title ="Detections"))


```

Event Data

```{r}
all_sensors_df <- vroom::vroom("all_sensors_df.csv")
online<-vroom::vroom(here::here("Event_Data/attendances.csv"))
park<-read.csv(here::here("Event_Data/qeop_events_list_from_0101192.csv"), stringsAsFactors = FALSE) #removing events where attendance = 0 as these seem to be very low key e.g. filming/photography events in the park

park <- park %>% 
  dplyr::mutate(In = as.POSIXct(In, format = "%d/%m/%y %H:%M"), Out = as.POSIXct(Out, format = "%d/%m/%y %H:%M")) %>%   
  dplyr::filter(Attendance != "0")

online <- online %>% 
  filter(event_type != "Tour")

online$date <- as.Date(online$date, format = "%d/%m/%Y")

dates <- data.frame(date = unique(all_sensors_df$date))
all_online<- merge(online, dates, all = TRUE, by = "date")
all_online$event_bin <- ifelse(is.na(all_online$event_type),0,1)

all_sensors_df <- merge(all_sensors_df, all_online[, c("date","attendance", "event_bin")], by = "date")
  
```



###Sorting the data out
```{r}

#dir <- here::here("model_output/")

dir <- here::here("model_output_filtered_df")

if (!dir.exists(here::here("model_output"))){
  dir.create(here::here("model_output"))
}

all_sensors_df$month_num<-as.numeric(all_sensors_df$month)


all_sensors_df$inactive_week[is.na(all_sensors_df$inactive_week)]<-0

all_sensors_df$event_bin <- as.factor(all_sensors_df$event_bin)

all_sensors_df <- all_sensors_df %>% 
  dplyr::select(date, hour_rnd, deployment_id, Lat, Lon, count_hour_dep_rnd, mean_temp, mean_humid, mean_wind, mean_wind_gust, precip_total, hours_inactive, inactive_week, month, sum_active, event_bin)
  
all_sensors_df_cc<-all_sensors_df[complete.cases(all_sensors_df),]


```

###Sorting the data out - filtering out data to exclude calls one hour before dusk and one hour after sunrise
```{r}

suns<-getSunlightTimes(date = as.Date(all_sensors_df_cc$hour_rnd),lat = 51.543523, lon = -0.016214 ,keep = c("sunrise","sunset"), tz = "UTC")

suns<-unique(suns)

all_sensors_df_cc <- merge(all_sensors_df_cc, suns, by = "date")

all_sensors_df_cc$sunrise_lim <- all_sensors_df_cc$sunrise + (1*60*60)
all_sensors_df_cc$sunset_lim <- all_sensors_df_cc$sunset - (1*60*60)

all_sensors_df_cc$deployment_id <- as.factor(all_sensors_df_cc$deployment_id)

all_sensors_df_cc <- all_sensors_df_cc %>% 
  filter(hour_rnd <= sunrise_lim | hour_rnd >= sunset_lim) %>% 
  filter(deployment_id != "1.1" & deployment_id != "6.1" & deployment_id != "11.1") %>% #high rates of false positives
  filter(deployment_id != "3.1" & deployment_id != "4.2" & deployment_id != "5.1"& deployment_id != "15.1")  #%>% #no record of false positive/false negative rates
 #filter(deployment_id != "4.1") 
```

###Fitting Models - Poisson

```{r}

fit_zipoisson <- glmmTMB(count_hour_dep_rnd~ mean_temp+ 
                              mean_wind + precip_total + 
                              event_bin + (1|deployment_id),   
                              data = all_sensors_df_cc,
                              ziformula = ~1,
                              dispformula = ~1,
                              family = poisson)

saveRDS(fit_zipoisson, paste0(dir,"/zi_poisson.RDA"))

fit_zipoisson <- readRDS(paste0(dir,"/zi_poisson.RDA"))

simulationOutput_pois <- simulateResiduals(fittedModel = fit_zipoisson, n = 250)

plot(simulationOutput_pois)

testResiduals(simulationOutput_pois)

testZeroInflation(simulationOutput_pois)

testDispersion(simulationOutput_pois)

```

###Fitting Models - Hurdle Model 1
```{r}
fit_hnbinom1 <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                             mean_wind + precip_total + 
                             event_bin + (1|deployment_id),   
                             data = all_sensors_df_cc,
                             ziformula=~1,
                             dispformula = ~1,
                             family=truncated_nbinom1)

saveRDS(fit_hnbinom1, paste0(dir,"/zin_hnbinom1.RDA"))

fit_hnbinom1 <- readRDS(paste0(dir,"/zin_hnbinom1.RDA"))

simulationOutput_hurd1 <- simulateResiduals(fittedModel = fit_hnbinom1, n = 250)

plot(simulationOutput_hurd1)

testResiduals(simulationOutput_hurd1)

testZeroInflation(simulationOutput_hurd1)

testDispersion(simulationOutput_hurd1)

```

###Fitting Models - Hurdle Model 2
```{r}
fit_hnbinom2 <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                             mean_wind + precip_total + 
                             event_bin + (1|deployment_id),   
                             data = all_sensors_df_cc,
                             ziformula= ~1,
                             dispformula = ~1,
                             family=truncated_nbinom2)

saveRDS(fit_hnbinom2, paste0(dir,"/zin_hnbinom2.RDA"))

fit_hnbinom2 <- readRDS(paste0(dir,"/zin_hnbinom2.RDA"))

simulationOutput_hurd2 <- simulateResiduals(fittedModel = fit_hnbinom2, n = 250)


plot(simulationOutput_hurd2)

testResiduals(simulationOutput_hurd2)

testZeroInflation(simulationOutput_hurd2)

testDispersion(simulationOutput_hurd2)

```

###Fitting Models - Negative binomial 1
```{r}

fit_zinbinom1 <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                             mean_wind + precip_total + 
                             event_bin + (1|deployment_id),   
                             data = all_sensors_df_cc,
                             ziformula= ~1,
                             dispformula = ~1,
                             family=nbinom1)

saveRDS(fit_zinbinom1, paste0(dir,"/zin_binom1.RDA"))

fit_zinbinom1 <- readRDS(paste0(dir,"/zin_binom1.RDA"))


simulationOutput_zbin1 <- simulateResiduals(fittedModel = fit_zinbinom1, n = 250)

testZeroInflation(simulationOutput_zbin1)

testDispersion(simulationOutput_zbin1)

testResiduals(simulationOutput_zbin1)

plotResiduals(all_sensors_df_cc$mean_temp, simulationOutput_zbin1$scaledResiduals,quantreg = T)
```

###Fitting Models - Negative binomial 2
```{r}

fit_zinbinom2 <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                              mean_wind + precip_total + 
                             event_bin + (1|deployment_id),   
                             data = all_sensors_df_cc,   
                             ziformula=~1,
                             family=nbinom2)

saveRDS(fit_zinbinom2, paste0(dir,"/zin_binom2.RDA"))

fit_zinbinom2 <- readRDS(paste0(dir,"/zin_binom2.RDA"))

simulationOutput_zbin2 <- simulateResiduals(fittedModel = fit_zinbinom2)

testZeroInflation(simulationOutput_zbin2)
testDispersion(simulationOutput_zbin2)

plotResiduals(all_sensors_df_cc$mean_temp, simulationOutput_zbin2$scaledResiduals,quantreg = T)
``` 

###Comparing models before digging deeper into model fit

```{r}
#AICtab(fit_zipoisson, fit_hnbinom1, fit_hnbinom2, fit_zinbinom1, fit_zinbinom2)

AICtab(fit_zipoisson, fit_zinbinom1, fit_zinbinom2)
```
###Fitting Models - Negative binomial 1 with deployment as var in dispformula

```{r}

fit_zinbinom1_dep <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                             mean_wind + precip_total + 
                             event_bin + (1|deployment_id),   
                             data = all_sensors_df_cc,
                             ziformula = ~1,
                             dispformula=~deployment_id,
                             family=nbinom1)

saveRDS(fit_zinbinom1_dep, paste0(dir,"/zin_binom1_dep.RDA"))

fit_zinbinom1_dep <- readRDS(paste0(dir,"/zin_binom1_dep.RDA"))


simulationOutput_zbin1_dep <- simulateResiduals(fittedModel = fit_zinbinom1_dep, n = 250)

#plot(simulationOutput_zbin1)

testZeroInflation(simulationOutput_zbin1_dep)

testDispersion(simulationOutput_zbin1_dep)

testResiduals(simulationOutput_zbin1_dep)
```

###Fitting Models - Negative binomial 1 with month as var in dispformula
```{r}

fit_zinbinom1_mon <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                             mean_wind + precip_total + 
                             event_bin + (1|deployment_id),   
                             data = all_sensors_df_cc,
                             ziformula = ~1,
                             dispformula=~month,
                             family=nbinom1)

saveRDS(fit_zinbinom1_mon, paste0(dir,"/zin_binom1_mon.RDA"))

fit_zinbinom1_mon <- readRDS(paste0(dir,"/zin_binom1_mon.RDA"))


simulationOutput_zbin1_mon <- simulateResiduals(fittedModel = fit_zinbinom1_mon, n = 250)

#plot(simulationOutput_zbin1)

testZeroInflation(simulationOutput_zbin1_mon)

testDispersion(simulationOutput_zbin1_mon)

testResiduals(simulationOutput_zbin1_mon)

```

###Fitting Models - Negative binomial 1 with deployment and month as vars in dispformula
```{r}

fit_zinbinom1_dep_mon <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                             mean_wind + precip_total + 
                             event_bin + (1|deployment_id),   
                             data = all_sensors_df_cc,
                             ziformula = ~1,
                             dispformula = ~ month + deployment_id,
                             family = nbinom1)

saveRDS(fit_zinbinom1_dep_mon, paste0(dir,"/zin_binom1_dep_mon.RDA"))

fit_zinbinom1_dep_mon <- readRDS(paste0(dir,"/zin_binom1_dep_mon.RDA"))


simulationOutput_zbin1_dep_mon <- simulateResiduals(fittedModel = fit_zinbinom1_dep_mon, n = 250)

#plot(simulationOutput_zbin1)

testZeroInflation(simulationOutput_zbin1_dep_mon)

testDispersion(simulationOutput_zbin1_dep_mon)

testResiduals(simulationOutput_zbin1_dep_mon)

```

###Fitting Models - Negative binomial 1 with deployment and month as vars in dispformula and ziformula

```{r}

fit_zinbinom1_dep_mon_both <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                             mean_wind + precip_total + 
                             event_bin + (1|deployment_id),   
                             data = all_sensors_df_cc,
                             ziformula = ~ month + deployment_id,
                             dispformula = ~ month + deployment_id,
                             family = nbinom1)

saveRDS(fit_zinbinom1_dep_mon_both, paste0(dir,"/zin_binom1_dep_mon_both.RDA"))

fit_zinbinom1_dep_mon_both <- readRDS(paste0(dir,"/zin_binom1_dep_mon_both.RDA"))


simulationOutput_zbin1_dep_mon_both <- simulateResiduals(fittedModel = fit_zinbinom1_dep_mon_both, n = 250)

#plot(simulationOutput_zbin1)

testZeroInflation(simulationOutput_zbin1_dep_mon_both)

testDispersion(simulationOutput_zbin1_dep_mon_both)

testResiduals(simulationOutput_zbin1_dep_mon_both)

```





###Fitting Models - Negative binomial 2 with deployment as var in dispformula
```{r}

fit_zinbinom2_disp <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                             mean_wind + precip_total + 
                             event_bin + (1|deployment_id),   
                             data = all_sensors_df_cc,   
                             ziformula=~1,
                             dispformula = ~deployment_id,
                             family=nbinom2)

saveRDS(fit_zinbinom2_disp, paste0(dir,"/zin_binom2_disp.RDA"))

fit_zinbinom2_disp <- readRDS(paste0(dir,"/zin_binom2_disp.RDA"))

simulationOutput_zbin2_disp <- simulateResiduals(fittedModel = fit_zinbinom2_disp, n = 250)

testZeroInflation(simulationOutput_zbin2_disp)
testDispersion(simulationOutput_zbin2_disp)

plotResiduals(all_sensors_df_cc$mean_temp, simulationOutput_zbin2_disp$scaledResiduals,quantreg = T)
```


```{r}

fit_zinbinom2_mon <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                             mean_wind + precip_total + 
                             event_bin + (1|deployment_id),   
                             data = all_sensors_df_cc,   
                             ziformula=~1,
                             dispformula = ~deployment_id+month,
                             family=nbinom2)


saveRDS(fit_zinbinom2_mon, paste0(dir,"/zin_binom2_mon.RDA"))

fit_zinbinom2_mon <- readRDS(paste0(dir,"/zin_binom2_mon.RDA"))


simulationOutput_zbin2_mon <- simulateResiduals(fittedModel = fit_zinbinom2_mon, n = 250)

testZeroInflation(simulationOutput_zbin2_mon)
testDispersion(simulationOutput_zbin2_mon)

plotResiduals(all_sensors_df_cc$mean_temp, simulationOutput_zbin2_mon$scaledResiduals,quantreg = T)

```

###Fitting Models - Negative binomial 2 with deployment and month as vars in dispformula
```{r}

fit_zinbinom2_disp_mon <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                             mean_wind + precip_total + 
                             event_bin + (1|deployment_id),   
                             data = all_sensors_df_cc,   
                             ziformula=~1,
                             dispformula = ~deployment_id+month,
                             family=nbinom2)


saveRDS(fit_zinbinom2_disp_mon, paste0(dir,"/zin_binom2_disp_mon.RDA"))

fit_zinbinom2_disp_mon <- readRDS(paste0(dir,"/zin_binom2_disp_mon.RDA"))


simulationOutput_zbin2_disp_mon <- simulateResiduals(fittedModel = fit_zinbinom2_disp_mon, n = 250)

testZeroInflation(simulationOutput_zbin2_disp_mon)
testDispersion(simulationOutput_zbin2_disp_mon)

plotResiduals(all_sensors_df_cc$mean_temp, simulationOutput_zbin2_disp_mon$scaledResiduals,quantreg = T)

``` 

###Fitting Models - Negative binomial 2 with deployment and month as vars in both dispformula and ziformula
```{r}

fit_zinbinom2_disp_mon_both <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                             mean_wind + precip_total + 
                             event_bin + (1|deployment_id),   
                             data = all_sensors_df_cc,   
                             ziformula=~deployment_id+month,
                             dispformula = ~deployment_id+month,
                             family=nbinom2)


saveRDS(fit_zinbinom2_disp_mon_both, paste0(dir,"/zin_binom2_disp_mon_both.RDA"))

fit_zinbinom2_disp_mon_both <- readRDS(paste0(dir,"/zin_binom2_disp_mon_both.RDA"))


simulationOutput_zbin2_disp_mon_both <- simulateResiduals(fittedModel = fit_zinbinom2_disp_mon_both, n = 250)

testZeroInflation(simulationOutput_zbin2_disp_mon_both)
testDispersion(simulationOutput_zbin2_disp_mon_both)

plotResiduals(all_sensors_df_cc$mean_temp, simulationOutput_zbin2_disp_mon_both$scaledResiduals,quantreg = T)

``` 


```{r}


AICtab(fit_zinbinom1_dep_mon, fit_zinbinom1, fit_zinbinom1_dep, fit_zinbinom1_mon, fit_zinbinom1_dep_mon_both, fit_zinbinom2, fit_zinbinom2_disp,fit_zinbinom2_mon, fit_zinbinom2_disp_mon, fit_zinbinom2_disp_mon_both )

plotResiduals(all_sensors_df_cc$mean_temp,simulationOutput_zbin1_dep_mon_both$scaledResiduals,quantreg = T)

mlist <- list(fit_zinbinom1_dep_mon, fit_zinbinom1, fit_zinbinom1_dep, fit_zinbinom1_mon, fit_zinbinom1_dep_mon_both, fit_zinbinom2, fit_zinbinom2_disp,fit_zinbinom2_mon, fit_zinbinom2_disp_mon, fit_zinbinom2_disp_mon_both )


```

```{r}

model = fit_zinbinom1_dep_mon_both 

sims=simulate(model, seed = 1, nsim = 1000)

simdatlist=lapply(sims, function(count){
  cbind(count, all_sensors_df_cc[,c('mean_temp', 'mean_wind', 'precip_total', 'event_bin', 'deployment_id', 'month')])
})

simdatsums=lapply(simdatlist, function(x){
  ddply(x, ~deployment_id+event_bin, summarize,
  mean_count=mean(count))
})

ssd=do.call(rbind, simdatsums)


real = ddply(all_sensors_df_cc, ~deployment_id+event_bin, summarize,
 mean_count=mean(count_hour_dep_rnd))


ggplot(ssd, aes(x = mean_count, color = event_bin)) +
  geom_density(adjust = 10) +
  facet_wrap( ~ deployment_id) +
  geom_point(data = real,
             aes(x = mean_count, y = 0.0025, color = event_bin),
             size = 2) +
  xlab("Predicted average hourly bat calls") + ylab(NULL)


```

```{r}

model = fit_zinbinom1


fit_zinbinom1_monde <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                             mean_wind + precip_total + 
                             event_bin + (1|deployment_id) + (1|month),   
                             data = all_sensors_df_cc,
                             ziformula= ~1,
                             dispformula = ~1,
                             family=nbinom1)

model = fit_zinbinom1_monde

all_sensors_df_cc$month_f <- factor(all_sensors_df_cc$month, levels=c('Jan','Feb','Mar','Apr','May','Jun','Jul','Aug','Sep','Oct','Nov','Dec'))

all_sensors_df_cc$bats_active_month <- NULL

all_sensors_df_cc$bats_active_month <- ifelse( all_sensors_df_cc$month == "May" | all_sensors_df_cc$month == "Jun" | all_sensors_df_cc$month == "Jul" | all_sensors_df_cc$month == "Aug" | all_sensors_df_cc$month == "Sep" | all_sensors_df_cc$month == "Oct", "awake", "hibernating")

sims=simulate(model, seed = 1, nsim = 1000)

simdatlist=lapply(sims, function(count){
  cbind(count, all_sensors_df_cc[,c('mean_temp', 'mean_wind', 'precip_total', 'event_bin', 'deployment_id', 'month', 'bats_active_month')])
})

simdatsums=lapply(simdatlist, function(x){
  # ddply(x, ~event_bin+bats_active_month, summarize,
  # mean_count=mean(count))
 x %>% 
  group_by(event_bin, bats_active_month) %>% 
  mutate(mean_count_hib = mean(count)) %>% 
  ungroup() %>% 
  group_by(month, event_bin) %>% 
  mutate(mean_count_month = mean(count))

  })

ssd=do.call(rbind, simdatsums)


real <- all_sensors_df_cc %>% 
  group_by(event_bin, bats_active_month) %>% 
  mutate(mean_count_hib = mean(count_hour_dep_rnd)) %>% 
  ungroup() %>% 
  group_by(month, event_bin) %>% 
  mutate(mean_count_month = mean(count_hour_dep_rnd))


ggplot(ssd, aes(x = mean_count_hib, color = event_bin)) +
  geom_density(adjust = 10) +
  facet_wrap(~ bats_active_month) +
  geom_point(data = real,
             aes(x = mean_count_hib, y = 0.0045, color = event_bin),
             size = 2) +
  xlab("Predicted average hourly bat calls") + ylab(NULL)+xlim(0,400)




ggplot(ssd[ssd$bats_active_month == "awake",], aes(x = mean_count_month, color = event_bin)) +
  geom_density(adjust = 10) +
  facet_wrap(~ month_f) +
  geom_point(data = real[real$bats_active_month == "awake",],
             aes(x = mean_count_month, y = 0.0045, color = event_bin),
             size = 2) +
  xlab("Predicted average hourly bat calls") + ylab(NULL)+xlim(0,400)


```










```{r}

m1 <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                             mean_wind + precip_total + 
                             event_bin + (1|deployment_id),   
                             data = all_sensors_df_cc,
                             ziformula = ~ month + deployment_id,
                             dispformula = ~ month + deployment_id,
                             family = nbinom1)

saveRDS(fit_zinbinom1_dep_mon_both, paste0(dir,"/zin_binom1_dep_mon_both.RDA"))

fit_zinbinom1_dep_mon_both <- readRDS(paste0(dir,"/zin_binom1_dep_mon_both.RDA"))


simulationOutput_zbin1_dep_mon_both <- simulateResiduals(fittedModel = fit_zinbinom1_dep_mon_both, n = 250)

#plot(simulationOutput_zbin1)

testZeroInflation(simulationOutput_zbin1_dep_mon_both)

testDispersion(simulationOutput_zbin1_dep_mon_both)

testResiduals(simulationOutput_zbin1_dep_mon_both)

```


```{r}
fit_zinbinom2_mon_circ <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                              mean_wind + precip_total + 
                              sin(month_num/12 * pi) + 
                              cos(month_num/12 * pi) +
                             (1|deployment_id),   
                             data = all_sensors_df,   
                              ziformula=~1,
                              family=nbinom2)

saveRDS(fit_zinbinom2, paste0(dir,"/zin_binom2.RDA"))


fit_hnbinom1 <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                              mean_wind + precip_total + 
                             (1|deployment_id),   
                             data = all_sensors_df,
                        ziformula=~1,
                        family=truncated_nbinom1)

saveRDS(fit_hnbinom1, paste0(dir,"/zin_hnbinom1.RDA"))


##Doesn't converge

fit_hnbinom2 <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                              mean_wind + precip_total + 
                             (1|deployment_id),   
                             data = all_sensors_df,
                        ziformula=~1,
                        family=truncated_nbinom2)

saveRDS(fit_hnbinom2, paste0(dir,"/zin_hnbinom2.RDA"))



AICtab(fit_zipoisson,fit_zinbinom1, fit_zinbinom2, fit_hnbinom1, fit_hnbinom2)



```















Distribution of daily calls over the year by species - some of the species names are spelt multiple ways, some wrong, some right.


####Figure 6: Distribution of total daily calls for each month, by species.  

```{r}
ggplot(all_sens_info, aes(x = month_ch, y = count_sp))+
  scale_y_continuous(trans = log10_trans(), breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x)))+
  labs(x = "Month", y = "Daily Detected Calls")+
  geom_boxplot()+
  facet_wrap(.~c1)+
  scale_x_discrete(labels=month.abb) +
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 14, angle= 45, hjust = 1),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```


####Figure 7: Distribution of total daily calls for each month, by genus.  

```{r}

all_sens_info$g1<-vapply(strsplit(as.character(all_sens_info$c1)," "), `[`, 1, FUN.VALUE=character(1))

all_sens_info<-all_sens_info %>%
  group_by(sensor_id,g1, date)%>%
  mutate(count_gen = n())%>%
  ungroup()

genus_plot<-ggplot(all_sens_info, aes(x = month_ch, y = count_gen))+
    scale_y_continuous(trans = log10_trans(), breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x)))+
  labs(x = "Month", y = "Daily Detected Calls")+
  geom_boxplot()+
  facet_wrap(.~g1)+
  scale_x_discrete(labels=month.abb) +
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 14, angle= 45, hjust = 1),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 20))

png("Annual_Calls_genus.png", width = 10, height = 8, units = 'in', res = 300)
genus_plot# Make plot
dev.off()


```

```{r}

all_sensors_active<-merge(all_active_df[, c("date", "deployment_id", "inactive_week")], all_sens_info, by = c("date", "deployment_id"))


all_sensors_active %>%
  filter(is.na(inactive_week))%>%
ggplot(aes(x = month_ch, y = count_gen))+
  geom_boxplot()+
   scale_y_continuous(trans = log10_trans(), breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x)))+
  labs(x = "Month", y = "Daily Detected Calls")+
  facet_wrap(.~as.factor(g1))+
  scale_x_discrete(labels=month.abb) +
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 14, angle= 45, hjust = 1),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 20))

```



```{r}

ggplot(all_sens_info, aes(p1, group = c1))+
  geom_histogram()+
  #scale_y_continuous(trans = "log1p")+
  #ylim(0,5000)+
  facet_wrap(~c1)



ggplot(all_sens_info, aes(p1, group = c1))+
  geom_histogram()+
  #scale_y_log10()+
  scale_y_continuous(breaks=c(1,10,100,1000,10000,100000, 1000000),trans = "log1p")+
  #ylim(0,5000)+
  ylab("Count (log1p)")+
  xlab("Classification Probability")+
  facet_wrap(~c1)



```
####Figure 8: Distribution of total daily calls for each month, by habitat type.

```{r}
all_sens_info<-all_sens_info %>%
  group_by(sensor_id,Habitat, date)%>%
  mutate(count_hab = n())%>%
  ungroup()

ggplot(all_sens_info, aes(x = month_ch, y = log10(count_hab)))+
  geom_boxplot()+
  facet_wrap(.~Habitat)+
  labs(x = "Month", y = "Log10 Daily Calls")+
  scale_x_discrete(labels=month.abb) +
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 14, angle= 45, hjust = 1),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```

####Figure 9: Distribution of total daily calls for each month, by deployment.

```{r}
all_sens_info<-all_sens_info %>%
  group_by(deployment_id, date)%>%
  mutate(count_sens = n())%>%
  ungroup()

ggplot(all_sens_info, aes(x = month_ch, y = log10(count_sens)))+
  geom_boxplot()+
  facet_wrap(.~as.numeric(deployment_id))+
  labs(x = "Month", y = "Log10 Daily Calls")+
  scale_x_discrete(labels=month.abb) +
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 12),
        axis.text.x = element_text(size = 12, angle= 45, hjust = 1),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

```



```{r,echo = FALSE, eval = FALSE}
library(suncalc)
library(lubridate)

QEOP_loc<-cbind(mean(unique(all_sens_info$Lat)), mean(unique(all_sens_info$Lon)))


suntimes<-getSunlightTimes(lat = QEOP_loc[1], lon = QEOP_loc[2], date = unique(as.Date(all_sens_info$date)), keep = c("sunrise", "sunset"), tz = "UTC")

suntimes$date<-as.Date(suntimes$date)

suntimes$sunrise<-if_else(suntimes$date < as.Date("2017-10-29") | (suntimes$date > as.Date("2018-03-24") & suntimes$date < as.Date("2018-10-28")), suntimes$sunrise - 3600 , suntimes$sunrise)

suntimes$sunset<-if_else(suntimes$date < as.Date("2017-10-29") | (suntimes$date > as.Date("2018-03-24") & suntimes$date < as.Date("2018-10-28")), suntimes$sunset - 3600 , suntimes$sunset)


suntimes$date<-as.Date(suntimes$date)
all_sens_info$date<-as.Date(all_sens_info$date)

df<-merge(suntimes, all_sens_info, by="date")
df$sunrise <- strftime(df$sunrise, format="%H:%M:%S")
df$sunrise <- as.POSIXct(df$sunrise, format="%H:%M:%S")

ggplot(df, aes(x = date, y = sunrise))+
  #geom_boxplot(aes(fill=Habitat))+ 
  geom_line()

#df$sunset_diff<-  as.numeric(df$sunset - df$timestamp)

#hist(df$sunset_diff/3600, main = "", xlab = "Hours Since Sunset")


```

```{r}

lapply(mlist, logLik)

cv_out <- cv.glm(glmfit = fit_zinbinom1_dep_mon, data = all_sensors_df_cc, K = 10)


k_folds <- dismo::kfold(all_sensors_df_cc, k = 4)

for(i in 1:4){
  
  train_data = all_sensors_df_cc[k_folds != i,]
  test_data = all_sensors_df_cc[k_folds == i,]
  
  
  model_update <- glmmTMB(count_hour_dep_rnd ~ mean_temp+ 
                             mean_wind + precip_total + 
                             event_bin + (1|deployment_id),   
                             data =  train_data,
                             ziformula = ~ month + deployment_id,
                             dispformula = ~ month + deployment_id,
                             family = nbinom1)
  
  prob <- predict(model_update, newdata=test_data, se.fit=TRUE, zitype="response")
  outcome <- as.numeric(prob>pcut)
  
  test_data$predFE = prob$fit
  test_data$predFE.min = prob$fit-1.96*prob$se.fit
  test_data$predFE.max = prob$fit+1.96*prob$se.fit
  
  real=ddply(train_data, ~mean_temp+mean_wind+precip_total+event_bin+deployment_id+month, summarize, m=mean(count_hour_dep_rnd))

  
}

```







