---
title: "QEOP Analysis"
author: "Fiona Spooner"
date: "August 8, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r}

library(lubridate)
library(sp)
library(glmmTMB)
library(bbmle)
library(DHARMa)
library(dplyr)
library(lubridate)
library(suncalc)
library(ggplot2)
library(car)
library(broom)
library(broom.mixed)
library(dotwhisker)

```

```{r,echo = FALSE, eval= FALSE}
all_sens_info<-read.csv("all_bat_calls.csv")

all_sens_info$timestamp<-as.POSIXct(all_sens_info$timestamp)

all_sens_info$uni_hr<-round_date(all_sens_info$timestamp, unit = "hour")

all_sens_info$deployment<-1
```

Changing the deployment of all sensor four records after 14th May 2018 to deploment 2
Update all deployments here#

```{r,echo = FALSE, eval= FALSE}
all_sens_info[as.Date(as.character(all_sens_info$date)) > as.Date(as.character("2018-05-14")) & all_sens_info$sensor_id == 4,]<-all_sens_info %>%
  filter(as.Date(as.character(date)) > as.Date("2018-05-14") & sensor_id == 4)%>%
  mutate(deployment=replace(deployment, deployment==1, 2), Lat = replace(Lat, Lat==51.5367, 51.536553), Lon = replace(Lon, Lon==-0.0128, -0.013169))

# all_sens_info %>%
# filter(sensor_id == 4 & date >= as.Date("2018-05-14"))

all_sens_info[as.Date(as.character(all_sens_info$date)) > as.Date("2018-08-07") & all_sens_info$sensor_id == 5,]<-all_sens_info %>%
  filter(as.Date(as.character(date)) > as.Date("2018-08-07") & sensor_id == 5)%>%
  mutate(deployment=replace(deployment, deployment==1, 2), Lat = replace(Lat, Lat==51.5362, 51.590616), Lon = replace(Lon, Lon==-0.0127, -0.0139243), Habitat = replace(Habitat, Habitat == "Grassland", "Duncan's Garden" ))


all_sens_info$deployment_id<-paste(all_sens_info$sensor_id, all_sens_info$deployment, sep = ".")
```



###need to add in deployment_id

```{r,echo = FALSE, eval= FALSE}
hourly_data<-all_sens_info %>%
  filter(deployment_id != "4.1" & deployment_id != "5.2")%>%
  group_by(deployment_id, Habitat, uni_hr) %>%
  mutate(hourly_count = n())%>%
  arrange(-hourly_count)%>%
  dplyr::select(date, Habitat, deployment_id, Lat, Lon, hourly_count, uni_hr)%>%
  distinct()%>%
  ungroup()
```
##adding in the hours where there were no bat calls


```{r,echo = FALSE, eval= FALSE}
all_hours<-seq(from = min(hourly_data$uni_hr), to = max(hourly_data$uni_hr), by = "hour")

all_deps<-rep(unique(hourly_data$deployment_id), each = length(all_hours))

habs<-unique(hourly_data[,c("deployment_id", "Habitat")])

all_df<-data.frame(all_hours, all_deps,hourly_count = 0)
all_df$all_deps<-as.character(all_df$all_deps)

all_hours_df<-merge(all_df, hourly_data, by.x = c("all_deps","all_hours"), by.y = c("deployment_id", "uni_hr"), all=TRUE)
all_hours_df<-unique(all_hours_df)


all_hours_df<-merge(all_hours_df, habs, by.x = "all_deps", by.y = "deployment_id")

all_hours_df$hourly_count.y[is.na(all_hours_df$hourly_count.y)]<-0

df<-dplyr::select(all_hours_df, c(all_deps, all_hours, hourly_count.y, Habitat.y))
colnames(df)<-c("deployment_id", "time_hour", "count", "Habitat")

```


```{r, echo = FALSE,eval= FALSE}
break_finder<-function(x){
  nl_out<-rep(x, each = x)
}

all_sensors_df<-NULL

for (i in unique(df$deployment_id)){
  
  test<-df[df$deployment_id == i, ]
  test<-arrange(test, time_hour)
  rl<-rle(test$count == 0)  
  bf_out<-sapply(rl$lengths, break_finder)
  test_na_run<-unlist(bf_out)
  #test_na_run[!is.na(test$count)]<-NA
  test$hours_inactive<-test_na_run
  all_sensors_df<-rbind(all_sensors_df,test)
  #print(i)
  
}

sensor_down<-which(all_sensors_df$hours_inactive >= 168)  ###finding runs where a sensor has been inactive for a week or longer


all_sensors_df$active<-1

all_sensors_df$active[sensor_down]<-0

```

###Removing sensors which were not assessed to have high levels of accuracy or were not assessed for this

```{r, echo = FALSE,eval= FALSE}


all_sensors_df$month<-month(all_sensors_df$time_hour)

all_sens<-all_sensors_df %>%
  filter(deployment_id != "1.1" & deployment_id != "6.1" & deployment_id != "11.1") %>% #high rates of false positives
  filter(deployment_id != "3.1" & deployment_id != "4.2" & deployment_id != "5.1"& deployment_id != "15.1")   #no record of false positive/false negative rates

```


##Removing hours that were 2 hours before or 2 hrs after sunset

```{r, echo = FALSE,eval= FALSE}
library(suncalc)
library(dplyr)

suns<-getSunlightTimes(date = as.Date(all_sensors_df$time_hour),lat = 51.543523, lon = -0.016214 ,keep = c("sunrise","sunset"), tz = "UTC")

suns<-unique(suns)

all_sensors_df$date<-as.Date(all_sensors_df$time_hour)

all_suns_df<-merge(all_sensors_df, suns, by = "date")

all_suns_df$sunrise_lim<-all_suns_df$sunrise + (2*60*60)
all_suns_df$sunset_lim<-all_suns_df$sunset - (2*60*60)

suns_sub<-all_suns_df

#suns_sub<-all_suns_df %>%
#  filter(time_hour < sunrise_lim | time_hour > sunset_lim & active ==1)

#saveRDS(all_sensors_df, "hourly_bat_counts_sun_data.RDS")

```

#Climate data extraction

```{r,echo = FALSE, eval= FALSE}
sensor_info<-read.csv("sensor_info.csv")
bats<-merge(suns_sub, sensor_info[,1:3], by= "deployment_id")

events<-read.csv(here::here("Event_Data/attendances.csv"), stringsAsFactors = FALSE)
events$date<-as.Date(events$Date, format = "%d-%m-%y")

events<-events[-1,]
events<-events[events$Type.of.Event != "Tour",]

#climate<-readRDS("QEOP_hourly_climate_data_precip_diff.RDS")
climate<-readRDS("QEOP_hourly_climate_data_2019_08_28.RDS")
climate$date<-date(climate$round_time)

bats_events<-merge(bats, events, by= "date", all = TRUE)
bats_events<-merge(bats_events, climate, by.x = c("date", "time_hour"), by.y = c("date","round_time"))

bats_events$event_bin<- ifelse(is.na(bats_events$Event),"No","Yes")
#bats_events$event_bin_nd<- ifelse(is.na(bats_events$Event),"No","Yes")

#bats_events$event_bin_nd<-c("No", bats_events$event_bin[-length(bats_events$event_bin)])

bats_events$date_mid<-as.POSIXct(bats_events$date, format = "%Y-%m-%d %H:%M:%S", tz = "UTC")
attr(bats_events$date_mid, "tzone") <- "UTC" 
bats_events$date_mid<-bats_events$date_mid+43200

#changing hours on event days to "No" if they are before midday
bats_events$event_bin[bats_events$event_bin == "Yes" & bats_events$time_hour < bats_events$date_mid]<-"No"


day_after_event<-unique(bats_events$date[bats_events$event_bin == "Yes"]+1)

#changing hours on the day after event days to "Yes" if they are before 2 hrs after sunrise

bats_events$event_bin[bats_events$date == day_after_event & bats_events$event_bin == "No" & bats_events$time_hour < bats_events$date_mid]<-"Yes"


bats_events$event_bin<-as.factor(bats_events$event_bin)
bats_events$month<-as.factor(month(bats_events$date))

roost<-data.frame(-0.0141001,51.541341) #location of roost near sensor 7
colnames(roost)<-c("x","y")
coordinates(roost)<- ~x+y

lola<-unique(na.omit(bats_events[,c("Lon", "Lat")]))
coordinates(lola)<- ~Lon+Lat

dist_roost<-spDistsN1(lola, roost, longlat = TRUE)

dist_df<-data.frame(lola, dist_roost)

bats_events<-merge( bats_events,dist_df, by = c("Lon", "Lat"))

bats_events$deployment_id<-as.factor(bats_events$deployment_id)
#bats_events$inv_dist<-1/bats_events$dist_roost

#bats_events<-bats_events[!is.na(bats_events$count),]
#bats_events$uid<-paste(bats_events$time_hour, bats_events$deployment_id, sep = "_")

bats_model<-dplyr::select(bats_events,c(count,time_hour,date,deployment_id, Habitat,hours_inactive,active,lat, lon,sunrise,sunset,event_bin,mean_temp,mean_humid,mean_wind,mean_wind_gust, precip_total, dist_roost))
#%>%filter(active  == 1)

bats_cc<-bats_model[complete.cases(bats_model),]

#write.csv(bats_cc, "hourly_bats_complete_cases_for_models.csv", row.names = FALSE)
#saveRDS(bats_cc, "hourly_bats_complete_cases_for_models_sun_subs_events_adj_precip_diff.RDS")
#saveRDS(bats_cc, "hourly_bats_complete_cases_for_models_2019_08_28.RDS")


```


Sliding window of climate data

```{r,echo = FALSE, eval= FALSE}

climate_lag<-function(time, lag){
  
    climate_sub<-climate%>%
                  filter(round_time >  time & round_time <= time+(lag*60*60))%>%
                  summarise(mean_temp_lag = mean(mean_temp, na.rm=TRUE), 
                            mean_hum_lag = mean(mean_humid, na.rm=TRUE),
                            mean_wind_sp_lag = mean(mean_wind, na.rm=TRUE), 
                            mean_wind_g_lag = mean(mean_wind_gust, na.rm=TRUE), 
                            total_precip_lag = sum(precip_total, na.rm=TRUE))
    
    colnames(climate_sub)<-gsub("lag",lag,colnames(climate_sub))
    
    df_out<-data.frame(time, climate_sub)  
    print(df_out)
    return(df_out)

}

clim_24_out<-lapply(X = unique(bats_cc$time_hour), FUN = climate_lag, lag = 24)
clim_24_out<-do.call("rbind", clim_24_out)

#clim_36_out<-lapply(X = unique(bats_model$time_hour), FUN = climate_lag, lag = 36)
#clim_36_out<-do.call("rbind", clim_36_out)

clim_48_out<-lapply(X = unique(bats_model$time_hour), FUN = climate_lag, lag = 48)
clim_48_out<-do.call("rbind", clim_48_out)

climm<-merge(clim_24_out, clim_48_out, by = "time")
#climm<-merge(climm, clim_48_out, by = "time")

bats_all<-merge(bats_cc, climm , by.x  = "time_hour", by.y = "time")

#saveRDS(bats_all, "hourly_bats_complete_cases_for_models_sun_subs_lag_clim.RDS")
#saveRDS(bats_all, "hourly_bats_complete_cases_for_models_sun_subs_lag_clim_events_adj.RDS")
saveRDS(bats_all, "hourly_bats_complete_cases_for_models_2019_08_28.RDS")

```

Filter out the sensors which we cannot use

```{r,echo = FALSE,}

#bats_all<-readRDS("hourly_bats_complete_cases_for_models_sun_subs_lag_clim.RDS")

#bats_all<-readRDS("hourly_bats_complete_cases_for_models_sun_subs_events_adj_precip_diff.RDS")
bats_all<-readRDS("hourly_bats_complete_cases_for_models_2019_08_28.RDS")

bats_all<-bats_all %>%
  filter(deployment_id != "1.1" & deployment_id != "6.1" & deployment_id != "11.1") %>% #high rates of false positives
  filter(deployment_id != "3.1" & deployment_id != "4.2" & deployment_id != "5.1"& deployment_id != "15.1") 

#%>%
#  filter(active == 1)#no record of false positive/false negative rates


#write.csv(bats_all, "bats_hourly_data.csv", row.names = FALSE)

#write.csv(bats_all, "bats_hourly_data_precip_diff.csv", row.names = FALSE)

#write.csv(bats_all, "bats_hourly_data_2019_08_28.csv")

```
Plot data

```{r,eval = FALSE}

bats_all$month<-month(bats_all$time_hour)
bats_all$hour<-hour(bats_all$time_hour)

bats_all<-bats_all[complete.cases(bats_all),]

sum_month<-bats_all%>%
  group_by(month, deployment_id)%>%
  summarise(sum_month = sum(count))

bats_all<-bats_all%>%
  arrange(dist_roost)

ggplot(bats_all, aes(log1p(count)))+
  geom_histogram()+
  facet_wrap(~deployment_id)
#  
# ggplot(bats_all, aes(x = time_hour, y = deployment_id))+
#   geom_line(size = log1p(bats_all$count))

ggplot(bats_all, aes(log1p(count)))+
  geom_histogram()+
  facet_wrap(~month)


sum_zero<-bats_all%>%
  group_by(month, deployment_id,dist_roost)%>%
  filter(count == 0)%>%
  summarise(sum_zero = n())

ggplot(sum_zero, aes(x = dist_roost, y = sum_zero))+
  geom_point()




check<-bats_all%>%
  filter(deployment_id == "2.1")%>%
  arrange(time_hour)


```


```{r}
#saveRDS(bats_all, "all_bats_data_inc_zeros.RDS")

#saveRDS(bats_all, "all_bats_data_inc_zeros_events_adj.RDS")

saveRDS(bats_all, "all_bats_data_inc_2019_08_28.RDS")

```

```{r}

#plot(bats_all[,c("count", "event_bin", "tempAvg", "windspeedAvg", "precipTotal")])


plot(bats_all[bats_all$hours_inactive <337,c("count", "event_bin", "mean_temp","mean_humid","mean_wind", "mean_wind_gust","precip_total")])

```

Models!


```{r, eval = FALSE}

dir<-"hourly_models_new_clim_year_mon"
dir.create(here::here(dir))

hours_inactive_limit = 337

#bats_all<-readRDS("all_bats_data_inc_zeros_events_adj_precip_diff.RDS")
bats_all<-readRDS("all_bats_data_inc_2019_08_28.RDS")


bats_all<-unique(bats_all)
bats_all$jday<-yday(bats_all$date)

bats_all$year<-as.factor(year(bats_all$date))
bats_all$month<-as.factor(month(bats_all$date))
bats_all$jday<-as.factor(bats_all$jday)
bats_all$hour<-as.factor(hour(bats_all$time_hour))

bats_all$deployment_id<-as.factor(bats_all$deployment_id)

bats_all$year_mon<-paste0(bats_all$year, bats_all$month)

#bats_all<-bats_all[bats_all$hours_inactive <= 337, ]
```


```{r}
bats_all %>% 
  group_by(month) %>% 
  summarise(mean_count = mean(count))

```


```{r}
fit_zipoisson <- glmmTMB(count~ event_bin+ mean_temp+ 
                              mean_wind + precip_total + 
                              (1|year_mon/hour)+ 
                        (1|deployment_id),   
                        data=bats_all,
                        ziformula=~1,
                        family=poisson)

saveRDS(fit_zipoisson, paste0(dir,"/zi_poisson.RDA"))


fit_zinbinom1 <- glmmTMB(count~ event_bin+ mean_temp+ 
                              mean_wind + precip_total + 
                            (1|year_mon/hour)
                        +(1|deployment_id),   
                        data=bats_all,
                        ziformula=~1,
                        family=nbinom1)

saveRDS(fit_zinbinom1, paste0(dir,"/zin_binom1.RDA"))

fit_zinbinom2<- glmmTMB(count~ event_bin+ mean_temp+ 
                              mean_wind + precip_total + 
                             (1|year_mon/hour)
                              #(1|month/hour)
                             +(1|deployment_id),   
                              data=bats_all,
                              ziformula=~1,
                              family=nbinom2)

saveRDS(fit_zinbinom2, here::here(paste0(dir,"/zin_binom2.RDA")))


fit_hnbinom1 <- glmmTMB(count~ event_bin+ mean_temp+ 
                              mean_wind + precip_total + 
                              (1|year_mon/hour) + (1|deployment_id), 
                        data=bats_all,
                        ziformula=~1,
                        family=truncated_nbinom1)

saveRDS(fit_hnbinom1, here::here(paste0(dir,"/zin_hnbinom1.RDA")))


##Doesn't converge

fit_hnbinom2 <- glmmTMB(count~  event_bin+ mean_temp+ 
                              mean_wind + precip_total + 
                              (1|year_mon/hour) + (1|deployment_id), 
                        data=bats_all,
                        ziformula=~1,
                        family=truncated_nbinom2)

saveRDS(fit_hnbinom2, here::here(paste0(dir,"/zin_hnbinom2.RDA")))


fit_zinbinom1_mon<- glmmTMB(count~ event_bin+ mean_temp+ 
                              mean_wind + precip_total + 
                              (1|year_mon/hour)+ (1|deployment_id),   
                              data=bats_all,
                              ziformula=~year_mon,
                              family=nbinom1)

saveRDS(fit_zinbinom1_mon, here::here(paste0(dir,"/zin_binom1_mon.RDA")))


fit_zinbinom2_mon<- glmmTMB(count~ event_bin+ mean_temp+ 
                              mean_wind + precip_total + 
                              (1|year_mon/hour)+(1|deployment_id),   
                              data=bats_all,
                              ziformula=~year_mon,
                              family=nbinom2)

saveRDS(fit_zinbinom2_mon, here::here(paste0(dir,"/zin_binom2_mon.RDA")))


fit_zinbinom2_jday_hour<- glmmTMB(count~ event_bin+ mean_temp+ 
                              mean_wind + precip_total + 
                              (1|jday:hour)+(1|deployment_id),   
                              data=bats_all,
                              ziformula=~1,
                              family=nbinom2)

fit_zinbinom2_jday_hour_mon<- glmmTMB(count~ event_bin+ mean_temp+ 
                              mean_wind + precip_total + 
                              (1|jday:hour)+(1|deployment_id),   
                              data=bats_all,
                              ziformula=~hour+year_mon,
                              family=nbinom2)


fit_zinbinom2_hjday<- glmmTMB(count~ event_bin+ mean_temp+ 
                              mean_wind + precip_total + 
                              (1|deployment_id),   
                              data=bats_all,
                              ziformula=~hour+jday,
                              family=nbinom2)





fit_zinbinom2_mjh<- glmmTMB(count~ event_bin+ mean_temp+ 
                              mean_wind + precip_total + 
                              (1|year_mon/jday/hour)
                             +(1|deployment_id),   
                              data=bats_all,
                              ziformula=~1,
                              family=nbinom2)

saveRDS(fit_zinbinom2_mjh, here::here(paste0(dir,"/zin_binom2_mjh.RDA")))




AICtab(fit_zipoisson,fit_zinbinom1, fit_zinbinom2, fit_hnbinom1, fit_hnbinom2,fit_zinbinom1_mon,fit_zinbinom2_mon,fit_zinbinom2_mjh)

```

```{r}

ggplot(bats_all, aes(x = as.numeric(jday), y = log(as.numeric(count))))+
  geom_point(alpha = 0.4)+
  facet_wrap(.~hour)

bats_all %>% 
  group_by(jday)%>%
  filter(count == 0 ) %>% 
  summarise(all = n()) %>% 
  ggplot(aes(x = jday, y = all))+
  geom_point()

```

With all hours - add hour to zeroinflation model



```{r}

fit_zipoisson<-readRDS(here::here("hourly_models_new_event//zi_poisson.RDA"))
fit_zinbinom1<-readRDS(here::here("hourly_models_new_event/zin_binom1.RDA"))
fit_zinbinom2<-readRDS(here::here("hourly_models_new_event/zin_binom2.RDA"))
fit_hnbinom1<-readRDS(here::here("hourly_models_new_event/zin_hnbinom1.RDA"))
fit_hnbinom2<-readRDS(here::here("hourly_models_new_event/zin_hnbinom2.RDA"))
fit_zinbinom1_mon<-readRDS(here::here("hourly_models_new_event/zin_binom1_mon.RDA"))
fit_zinbinom2_mon<-readRDS(here::here("hourly_models_new_event/zin_binom2_mon.RDA"))
fit_zinbinom2_mon_jdrn<-readRDS(here::here("hourly_models_new_event/zin_binom2_mon_jdrn.RDA"))
fit_zinbinom2_mon_jdr<-readRDS(here::here("hourly_models_new_event/zin_binom2_mon_jdr.RDA"))
fit_zinbinom2_jday<-readRDS(here::here("hourly_models_new_event/zin_binom2_jday.RDA"))
#fit_zinbinom2_jdayq <-readRDS(here::here("hourly_models_new_event/zin_binom2_jdayq.RDA"))
#fit_zinbinom2_dist_int_mo<-readRDS(here::here("hourly_models_new_event/zin_binom2_dist_int_mo.RDA"))
#fit_olre<-readRDS(here::here("hourly_models_new_all_hours/zin_olre_24.RDA"))

AICtab(fit_zipoisson,fit_zinbinom1,fit_zinbinom2,fit_hnbinom2, fit_zinbinom1_mon,fit_zinbinom2_mon, fit_zinbinom2_mon_jdrn,fit_zinbinom2_mon_jdr,fit_zinbinom2_jday,fit_zinbinom2_jdayfq)

# fit_zipoisson_h<-readRDS(here::here("hourly_models_new_all_hours/zi_poisson_24.RDA"))
# fit_zinbinom1_h<-readRDS(here::here("hourly_models_new_all_hours/zin_binom1_24.RDA"))
# fit_zinbinom2_h<-readRDS(here::here("hourly_models_new_all_hours/zin_binom2_24.RDA"))
# fit_hnbinom1_h<-readRDS(here::here("hourly_models_new_all_hours/zin_hnbinom1_24.RDA"))
# fit_hnbinom2_h<-readRDS(here::here("hourly_models_new_all_hours/zin_hnbinom2_24.RDA"))
# fit_zipoisson_dist_h<-readRDS(here::here("hourly_models_new_all_hours/zin_poisson_dist_24.RDA"))
# fit_zinbinom1_mon_h<-readRDS(here::here("hourly_models_new_all_hours/zin_binom1_mon_24.RDA"))
# fit_zinbinom2_mon_h<-readRDS(here::here("hourly_models_new_all_hours/zin_binom2_mon_24.RDA"))
# fit_zinbinom1_dist_h<-readRDS(here::here("hourly_models_new_all_hours/zin_binom1_dist_24.RDA"))
# fit_zinbinom2_dist_h<-readRDS(here::here("hourly_models_new_all_hours/zin_binom2_dist_24.RDA"))
# fit_zinbinom1_dist_int_mo_h<-readRDS(here::here("hourly_models_new_all_hours/zin_binom1_dist_int_mo_24.RDA"))
# #fit_zinbinom2_dist_int_mo_h<-readRDS(here::here("hourly_models_new_all_hours/zin_binom2_dist_int_mo_24.RDA"))


AICtab(fit_zipoisson,fit_zinbinom1,fit_zinbinom2,fit_hnbinom2,fit_zipoisson_dist, fit_zinbinom1_mon,fit_zinbinom2_mon,fit_zinbinom1_dist,fit_zinbinom2_dist,fit_zinbinom1_dist_int_mo, fit_zinbinom2_dist_int_mo,fit_zipoisson_h,fit_zinbinom1_h,fit_zinbinom2_h,fit_hnbinom2_h,fit_zipoisson_dist_h, fit_zinbinom1_mon_h,fit_zinbinom2_mon_h,fit_zinbinom1_dist_h,fit_zinbinom2_dist_h,fit_zinbinom1_dist_int_mo_h,fit_zinbinom2_jday,fit_zinbinom2_jdayq, fit_zinbinom2_mon_jdr,fit_zinbinom2_mon_jdrn)


```



```{r}
bats_all<-readRDS("all_bats_data_inc_zeros.RDS")

dir.create(here::here("hourly_models_new_all_hours"))

bats_all$month<-as.factor(bats_all$month)
bats_all$hour<-as.factor(bats_all$hour)

m1<-fit_zinbinom2_mon


sr <- simulateResiduals(m1)
plot(sr)


car::Anova(m1)

t1 <- broom.mixed::tidy(m1, conf.int = TRUE)

t1_count<-t1[t1$component == "cond",]

t1_zinf<-t1[t1$component == "zi",]

m_est<-exp(t1_count$estimate)
m_cl<-exp(t1_count$conf.low)
m_hl<-exp(t1_count$conf.high)

m_ests<-data.frame(m_est, m_cl, m_hl)


zi_est<-exp(t1_zinf$estimate)/(1+exp(t1_zinf$estimate))
zi_cl<-exp(t1_zinf$conf.low)/(1+exp(t1_zinf$conf.low))
zi_hl<-exp(t1_zinf$conf.high)/(1+exp(t1_zinf$conf.high))

zi_ests<-data.frame(zi_est, zi_cl, zi_hl)

```


```{r,eval = FALSE}
source("StepbyStepGuide.R")


#################################
# Quantifying Point Estimate of Overdispersion
#################################

#Function to calculate a point estimate of overdispersion from a mixed model object
od.point<-function(modelobject){
	x<-sum(resid(modelobject,type="pearson")^2)
	rdf<-summary(modelobject)$AICtab[5]
	return(x/rdf)
}

od.point(m1)
	
#################################
# Quantifying Overdispersion Through Parametric Bootstrap
#################################

#Function to pass to parametric bootstrap function 'bootMer' that calculates the sum of squared Pearson residuals (required for 'od' function)
FUN <- function(fit) {
    #return(fixef(fit))
    x<-resid(fit,type="pearson")
    return(sum(x^2))
}	

#Function To Calculate Ratio of Model SS to Mean Parametric Bootstrap SS ('bias')
od<-function(bootobject){
	biasvals<-bootobject $t0/bootobject[2]$t
	bias<-mean(biasvals,na.rm=T)
	intervals<-quantile(biasvals,c(0.025,0.975),na.rm=T)
	dat<-c(bias,intervals)
	return(dat)
}


#Parametric bootstrap of the model - requires 'FUN' from above
library(boot) #require d to inspect results
library(lme4)

m1boot<-bootMer(m1,FUN,1)
m1boot

#Calculate Dispersion Parameter - uses "OD" function above
od(m1boot)


```

```{r}

summary(fit_zinbinom2)
ranef(fit_zinbinom2)


fit_zinbinom2b<-update(fit_zinbinom2, . ~ . -precipTotal)
summary(fit_zinbinom2b)

fit_zinbinom2c<-update(fit_zinbinom2b, . ~ . - mean_temp_24 - mean_wind_sp_24 - mean_wind_g_24  -total_precip_24)


summary(fit_zinbinom2c)
ranef(fit_zinbinom2c)
```



48 hours

```{r, eval = FALSE, echo = FALSE}


fit_zipoisson <- glmmTMB(count~ event_bin+ tempAvg+
                        windgustAvg + 
                        precipTotal + mean_temp_48+mean_wind_sp_48+
                        mean_wind_g_48+total_precip_48+
                        (1|deployment_id),   
                        data=bats_all,
                        ziformula=~1,
                        family=poisson)

saveRDS(fit_zipoisson, here::here("hourly_models_new/zi_poisson_48.RDA"))


fit_zinbinom1 <- glmmTMB(count~ event_bin+ tempAvg+
                        windgustAvg + 
                        precipTotal+mean_temp_48+mean_wind_sp_48+
                        mean_wind_g_48+total_precip_48+(1|deployment_id),   
                        data=bats_all,
                        ziformula=~1,
                        family=nbinom1)

saveRDS(fit_zinbinom1, here::here("hourly_models_new/zin_binom1_48.RDA"))


fit_zinbinom2 <- glmmTMB(count~ event_bin+ tempAvg+
                        windgustAvg + 
                        precipTotal + mean_temp_48+mean_wind_sp_48+
                        mean_wind_g_48+total_precip_48+(1|deployment_id),   
                        data=bats_all,
                        ziformula=~1,
                        family=nbinom2)

saveRDS(fit_zinbinom2, here::here("hourly_models_new/zin_binom2_48.RDA"))

fit_hnbinom1 <- glmmTMB(count~ event_bin+ tempAvg+
                        windgustAvg + 
                        precipTotal + mean_temp_48+mean_wind_sp_48+
                        mean_wind_g_48+total_precip_48+(1|deployment_id), 
                        data=bats_all,
                        ziformula=~1,
                        family=truncated_nbinom1)

saveRDS(fit_hnbinom1, here::here("hourly_models_new/zin_hnbinom1_48.RDA"))

##Doesn't converge

fit_hnbinom2 <- glmmTMB(count~  event_bin+ tempAvg+
                        windgustAvg + 
                        precipTotal + mean_temp_48+mean_wind_sp_48+
                        mean_wind_g_48+total_precip_48+(1|deployment_id), 
                        data=bats_all,
                        ziformula=~1,
                        family=truncated_nbinom2)

saveRDS(fit_hnbinom2, here::here("hourly_models_new/zin_hnbinom2_48.RDA"))

fit_zipoisson_dist <- glmmTMB(count~ event_bin+ tempAvg+
                              windgustAvg + precipTotal + 
                              mean_temp_48+mean_wind_sp_48+
                              mean_wind_g_48+total_precip_48+(1|deployment_id),   
                              data=bats_all,
                              ziformula=~dist_roost,
                              family=poisson)

saveRDS(fit_zipoisson_dist, here::here("hourly_models_new/zin_poisson_dist_48.RDA"))

fit_zinbinom1_dist <- glmmTMB(count~ event_bin+ tempAvg+
                              windgustAvg + precipTotal + mean_temp_48+
                              mean_wind_sp_48 + mean_wind_g_48+
                              total_precip_48+(1|deployment_id),   
                              data=bats_all,
                              ziformula=~dist_roost,
                              family=nbinom1)

saveRDS(fit_zinbinom1_dist, here::here("hourly_models_new/zin_binom1_dist_48.RDA"))


fit_zinbinom1_mon<- glmmTMB(count~ event_bin+ tempAvg+
                              windgustAvg + precipTotal + mean_temp_48+
                              mean_wind_sp_48 + mean_wind_g_48+
                              total_precip_48+(1|deployment_id),   
                              data=bats_all,
                              ziformula=~month,
                              family=nbinom1)

saveRDS(fit_zinbinom1_mon, here::here("hourly_models_new/zin_binom1_dist_48.RDA"))



fit_zinbinom2_dist <- glmmTMB(count~ event_bin+ tempAvg+
                              windgustAvg + precipTotal + mean_temp_48+
                              mean_wind_sp_48 + mean_wind_g_48+total_precip_48+
                              (1|deployment_id), data=bats_all,
                              ziformula=~dist_roost,
                              family=nbinom2)

saveRDS(fit_zinbinom2_dist, here::here("hourly_models_new/zin_binom2_dist_48.RDA"))

fit_hnbinom1_dist <- glmmTMB(count~ event_bin+ tempAvg+
                             windgustAvg + 
                             precipTotal + mean_temp_48+mean_wind_sp_48+
                             mean_wind_g_48+total_precip_48+(1|deployment_id), 
                             data=bats_all,
                             ziformula=~dist_roost,
                             family=truncated_nbinom1)

saveRDS(fit_hnbinom1_dist, here::here("hourly_models_new/zin_hnbinom1_dist_48.RDA"))

###Doesn't converge

fit_hnbinom2_dist <- glmmTMB(count~ event_bin+ tempAvg+
                        windgustAvg + 
                        precipTotal + mean_temp_48+mean_wind_sp_48+
                        mean_wind_g_48+total_precip_48+(1|deployment_id), 
                        data=bats_all,
                        ziformula=~dist_roost,
                        family=truncated_nbinom2)

saveRDS(fit_hnbinom2_dist, here::here("hourly_models_new/zin_binom2_dist_48.RDA"))


fit_zinbinom1_dist_int_mo <- glmmTMB(count~ event_bin+ tempAvg+
                                    windgustAvg + precipTotal + mean_temp_48 + 
                                    mean_wind_sp_48 +mean_wind_g_48+total_precip_48+
                                    (1|deployment_id), data=bats_all,
                                    ziformula=~dist_roost+month,
                                    family=nbinom1)

saveRDS(fit_zinbinom1_dist_int_mo, here::here("hourly_models_new/zin_binom1_dist_int_mo_48.RDA"))



bats_all$ID<-1:nrow(bats_all)


fit_olre <- glmmTMB(count~ event_bin+ tempAvg+
                    windgustAvg + 
                    precipTotal+ mean_temp_48+mean_wind_sp_48+
                    mean_wind_g_48+total_precip_48+(1|deployment_id)+
                    (1|ID), data=bats_all,
                    family=poisson)

#doesn't converge
saveRDS(fit_olre, here::here("hourly_models_new/zin_olre_48.RDA"))



AICtab(fit_zipoisson,fit_zinbinom1,fit_zinbinom2,fit_hnbinom1,fit_hnbinom2, fit_zipoisson_dist,fit_zinbinom1_dist, fit_zinbinom1_mon,
       fit_zinbinom2_dist,fit_hnbinom1_dist ,fit_hnbinom2_dist,fit_zinbinom1_dist_int_mo, fit_olre)



AICtab(fit_zipoisson,fit_zinbinom1,fit_zinbinom2,fit_hnbinom2, fit_zipoisson_dist,fit_zinbinom1_dist, fit_zinbinom1_mon,
       fit_zinbinom2_dist,fit_hnbinom2_dist,fit_zinbinom1_dist_int_mo, fit_olre)

```





```{r}

bats_all %>%
  group_by(month)%>%
  summarise(mean_calls = mean(count))


bats_all %>%
  group_by(month)%>%
  summarise(num_calls = n(),mean_calls = mean(count))


```